Assertion Contracts

### 2024-07-23 papers/assertion-contract/assertion_contract_app/paper.tex
Major revise

% APLAS 2021: Regular research papers should not exceed 18 pages in
% the Springer LNCS format(LaTeX template), including bibliography and
% figures.
% Lightweight double-blind: Author names and institutions must be
% omitted and References to the authors’ own related work should be in
% the third person 
%
\documentclass[runningheads]{llncs}
\pdfoutput=1
%\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{graphicx}
%\usepackage{fixme}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{titling}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{shapes.geometric, arrows}

@@

To operationalize these ideas, we suggest a practical model that addresses security concerns. We also implemented a prototype of the proposed protocol and conducted a cost analysis to demonstrate the advantages of our method in terms of cryptocurrency, proving its practical utility
 \keywords{}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
\section{Primaries}
\label{sec:primaries}

\section{Distributed Assertion Protocol}
\label{sec:approach}
We propose a novel method for verifying parameter assertions in smart contracts on the blockchain. Our approach distributes the assertion verification process and moves it off-chain, with only the verification results being submitted to the blockchain.

In this distributed process, each validator attempts to identify a counterexample to the assertion. Upon finding one, the validator submits the counterexample on-chain. Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points.

To implement this idea, we propose a proof-of-work-based incentivization method in which validators are rewarded for discovering counterexamples, and some are rewarded for their computational efforts, thus encouraging participation in the distributed verification process.

\subsection{Distributed assertions verification process}
In the context of a domain $A$ and a predicate $P$ on $A$, an assertion is formalized using the universal quantifier as follows:
\begin{gather}
  \label{eq:1}
\forall a \in A. P_{a}
\end{gather}

@@

@@

Our approach aims to alleviate this by distributing the negation of the assertion to validators. Each validator endeavors to find a counterexample of the assertion using this negation. Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied $\neg P_{a}$. When a counterexample is found, the validator submits it, which is then re-verified on-chain.

Since only one specific point is checked on-chain, the amount of gas required for the computation to check the counterexample is likely to be significantly less than verifying the entire assertion directly on-chain.

@@

\noindent each validator try to genarate  a
random $n$ in the range $2 \le n \le 
\sqrt p$ and checking whether $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the validator found a counterexample.

An other example, consider a contract that takes a sorted array of integers.
\begin{lstlisting}[numbers=none]
contract Sorted {
  function find (int[50] a, int v) public {
    // assume a is sorted
  }
}
\end{lstlisting}
The explicit assertion would be
\begin{gather}\label{eq:1}
  (\forall k) (0\le k <49) \Rightarrow a[k] \le a[k+1]
\end{gather}
While we can check this contract in $O(1)$ time, the constant factor is big! So we
consider its negation.
\begin{displaymath}
  (\exists k) (0\le k <49) \wedge a[k] > a[k+1]
\end{displaymath}
Each validator attempts to find the number $k$ such that the negation is true for such $k$, then the validator has found a counterexample for the sortedness of the array.
\subsection{Proof-of-work-based incentivization method}
Finding a counterexample is rewarded, incentivizing validators, but comes at the cost of computing resources. Instances of finding a counterexample may be rare, as callers typically avoid passing invalid parameters into the blockchain. If no counterexample emerges, the verification accuracy depends on the number of wisepoints generated to negate the assertion, with more validators increasing the certainty.

Encouraging validators to engage in the verification process even without discovering a counterexample is crucial. Therefore, it is necessary to incentivize this effort. Moreover, it is logical to reward only a portion of the computational effort required. A significant concern arises regarding how to ensure that validators perform the verification computation off-chain to receive the reward, even when no counterexample is foundward.

\subsubsection{Outlines}
We propose a proof-of-work-based method to incentivize participants in the distributed verification process. The proposed approach is outlined as follows:

\begin{itemize}
\item There are two ways to reward validators to encourage their participation: to discover a counterexample, and to provide computational proof that they have executed the program to search for a counterexample, even if none is found.
\item To prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.
\item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
\item Because the rewards may be limited in quantity, validators are motivated to swiftly verify the parameters to claim the reward before others do so.
\end{itemize}
\subsubsection{Computation Proof}
The next step is to devise a computation proof to incentivize computational effort by utilizing the proof-of-work concept. We introduce a target hash $t$ that sets the required difficulty level to earn the reward. The objective of the validator is to generate a computation that produces a hash smaller than or equal to the target hash $t$.

A key challenge is reproducing the computation proof off-chain to on-chain. To address this, we introduce a seed $s$ in each verification process. Let $n$ denote the size of domain $A$. Each number $i$ in the range $[1, n]$ corresponds to an element in $A$. The seed $s$ is reduced modulo $n$ to obtain $i$, which is associated with an element $a$ in $A$.
\paragraph{Estimate the number of seeds:} We first estimate the number of seeds needed to find a counterexample with a given expected probability.

Let's assume the unsatisfied element is only at the first element $a_0$ in $A$, the size of the domain is $n$, and the number of seeds is $m$. Each seed independently has a probability of $1/n$ to detect the problem and a probability of $\frac{n-1}{n}$ not to detect the problem. Hence, if we assume that each seed associated with an element $a$ in $A$ is chosen independently from a uniform distribution, the probability that no validator checks the element $a_0$ converges to $0$ as the number of seeds approaches infinity:

@@

Depending on the expected probability to detect the problem, the number of seeds to generate can be determined. Assume that $p$ is the probability of finding at least one counterexample. To calculate the number of seeds $m$ needed to achieve a given expected probability $p$ of finding a counterexample, we can use the complementary probability. We have:
\begin{itemize}
\item The probability of a single seed failing to find a counterexample is $\frac{n-1}{n}$.
\item The probability of all $m$ seeds failing to find a counterexample is $\left(\frac{n-1}{n}\right)^m$.
\item Therefore, the probability of at least one of the $m$ seeds finding a counterexample is:
\[
p = 1 - \left(\frac{n-1}{n}\right)^m
\]
\end{itemize}

@@

\[
\frac{2^{256} - 1}{m}
\]

\paragraph{Find a seed:}
The sequence of operations to find a seed can be described by the following steps:
\begin{enumerate}
\item Generate a random seed $s$: 
\begin{align}
s \in \mathbb{N} 
\end{align}
where $s$ is a random natural number.
\item Calculate $n$ as the size of the domain $A$: 
\begin{align}
n = |A|
\end{align}
where $\mid A \mid$ denotes the number of elements in the domain $A$.
\item Determine $i \in [1, n]$ using the modulo operation:
\begin{align}
i = (s \mod n) + 1
\end{align}
\item Find the corresponding element $a$ in $A$:
\begin{align}
a=A[i]
\end{align}
where $A[i]$ denotes the $i$-th element in $A$.
\item Perform the negation check $\neg P_{a}$ to detect a counterexample if any.

\item Calculate the hash \( t_s \) corresponding to the seed \( s \):
\begin{align}
t_s = \text{hash}(s, \text{eval}(\neg P_{a}))
\end{align}
where \(\text{hash}\) is the hash function and \(\text{eval}\) is the function that returns the significant components of the evaluation of the negation \(\neg P_{a}\).

For example, it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \(a[i] < a[i+1]\) in the sorted array example.
\item Compare \( t_s \) to the target hash to determin whether it is a reward computation.
\end{enumerate}

%Consequently, each seed $s$ is linked with an element $a$ in the domain $A$, followed by the evaluation of the negation of the assertion $\neg P_{a}$.

@@

\begin{enumerate}
\item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
\item Caller exploitation: A caller might exploit the system by running the negation check privately to identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators. 
\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
\item Reward manipulation: A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
\end{enumerate}
\subsection{Overview architect}
This section presents a practical model that unifies theoretical principles and addresses the previously mentioned security concerns. The architectural design of this model is depicted in Figure \ref{fig.architect}. The model consists of two main entities: an on-chain assertion contract and off-chain validator contract. In our practical model, three distinct actors play key roles.
\begin{itemize}
\item[•] Owner: responsible for deploying and overseeing both on-chain and off-chain contracts.
\item[•] Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
\item[•] Validators: tasked with validating parameters and ensuring the integrity of the verification process.
\end{itemize}

@@

In some applications, multiple computational proofs may be allowed. This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.

@@

For our offline distributed verification method, let's assume that the parameter is valid, and now we consider the cost to verify the parameter and perform the actual work. Let $m$ be the number of proofs required to ensure the correctness of the parameter. Thus, the offline method costs the gas for submitting the parameter, the gas to store the parameter (or its hash), $m$ times the gas to submit the seed, check the condition of the parameter point associated with the seed, the gas to compute the hash and compare it with the target hash, and of course the gas to run the computation of the actual work.

@@

\begin{equation}
G_{off} = G_{parameter} + G_{storage} + m \cdot (G_{seed} + G_{check} + G_{hash}) + G_{run}
\end{equation}

\begin{itemize}
    \item \( G_{parameter} \): Intrinsic gas for submitting the parameter.
    \item \( G_{storage} \): Gas for storing the parameter or its hash.
    \item \( G_{seed} + G_{check} + G_{hash} \): Gas for each of the \( m \) seeds to:
    \begin{itemize}
        \item Submit the seed (\( G_{seed} \)).
        \item Check the condition of the parameter point associated with the seed (\( G_{check} \)).
        \item Compute the hash and compare it with the target hash (\( G_{hash} \)).
    \end{itemize}
    \item \( G_{run} \): Gas for performing the actual work (computation).
\end{itemize}

@@

\paragraph*{Parameter Checking}
\begin{itemize}
    \item In the on-chain method, the parameter check cost is \( n \cdot G_{check} \), where \( n \) is the size of the parameter.
    \item In the offline method, this cost is \( m \cdot G_{check} \), where \( m \) is the number of seeds. Typically, \( m \) is significantly smaller than \( n \), as seeds represent a subset of checks.
\end{itemize}

\paragraph*{Additional Costs in the Offline Method}
\begin{itemize}
    \item The offline method includes \( m \cdot G_{seed} \) for submitting each seed.
    \item It also includes \( m \cdot G_{hash} \) for computing and comparing hashes, which the on-chain method does not explicitly incur.
\end{itemize}

@@

Let \( G_{m} \) be the sum of the gas costs to perform \( m \) times the parameter checkpoint:
\[
G_{m} = m \cdot (G_{seed} + G_{check} + G_{hash})
\]

In case the base gas does not contain the storage gas, then the \( G_m \) gas includes it.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \begin{axis}[
        title={Gas Consumption Chart},
        xlabel={Parameter size},
        ylabel={Gas},
        grid=both,
        major grid style={line width=.2pt,draw=gray!50},
        minor grid style={line width=.1pt,draw=gray!20},
        xtick={1,2,3,4,5,6,7,8},
        xticklabels={1,2,3,,,,n,},
        ytick={1,2,3,4,5,6,7,8},
        yticklabels={$G_{base} + G_{check}$,$G_{base} + 2 \cdot G_{check}$, $G_{base} + 3 \cdot G_{check}$,,$G_{base}+ G_m$,,$G_{base} + n \cdot G_{check}$,},
    ]
      \addplot[
        color=red,
        mark=square,
        ]
        coordinates {
        (1,1)(2,2)(3,3)(4,4)(5,5)(6,6)(7,7)
        };
        % Add custom labels as nodes
      %\node at (axis cs:1,1) [anchor=north] {$(1, m)$};
      %\node at (axis cs:2,2) [anchor=north] {$(2, g_3)$};
      %\node at (axis cs:3,3) [anchor=north] {$(3, a)$};
      %\node at (axis cs:4,4) [anchor=north] {$(4, b)$};
      %\node at (axis cs:5,5) [anchor=north] {$(5, c)$};

@@

%          \addplot[
%         color=blue,
%         mark=square,
%         ]
%         coordinates {
%         (1,5)(2,5)(3,5)(4,5)(5,5)(6,5)(7,5)
%         };
%     \end{axis}
%   \end{tikzpicture}
%   \caption{Gas comparation (non-storage)}
%   \label{fig:gas_compare_nonstorage}
% \end{figure}
Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks from \( n \) to \( m \). However, the exact cost-effectiveness depends on the relative sizes of \( n \) and \( m \), the parameter storing gas, and the specific gas costs of \( G_{seed} \) and \( G_{hash} \).
\section{Domain Specification Language for Assertion}
\note{To discuss: if it make sense to design}
\section{Converter - Generating an Assertion Contracts} 
\note{To discuss: if it make sense to implement}
\section{Prototype Implementations}
\note{TODO}
\subsection{Sorted array}
%There are two possible data structures for storing such records: map and array. For example, if we assume that a caller can submit only one parameter at a time, we can use a map that associates the caller's address with the parameter's hash and timestamp.
%\begin{lstlisting}[numbers=none]
%   struct Parameter {
%        bytes32 p_hash;
%        uint256 timestamp;
%    }
% mapping (address => Parameter) public parameters;
%\end{lstlisting}

>>>>

% APLAS 2021: Regular research papers should not exceed 18 pages in
% the Springer LNCS format(LaTeX template), including bibliography and
% figures.
% Lightweight double-blind: Author names and institutions must be
% omitted and References to the authors’ own related work should be in
% the third person 
%
\documentclass[runningheads]{llncs}
\pdfoutput=1
%\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{graphicx}
%\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{graphicx}
%\usepackage{fixme}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{titling}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{comment}

@@

To operationalize these ideas, we suggest a practical model that addresses security concerns. We also implemented a prototype of the proposed protocol and conducted a cost analysis to demonstrate the advantages of our method in terms of cryptocurrency, proving its practical utility
 \keywords{}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}

\section{Primaries}
\label{sec:primaries}

\section{Distributed Assertions Verification Process}
\label{sec:approach}
\subsection{Assertions verification problem}
In the context of a domain $A$ and a predicate $P$ on $A$, an assertion is formalized using the universal quantifier as follows:
\begin{gather}
  \label{eq:1}
\forall a \in A. P_{a}
\end{gather}

@@

\subsection{Distributed verification method}
We propose a novel method for verifying parameter assertions in smart contracts on the blockchain. Our approach distributes the assertion verification process and moves it off-chain, with only the verification results being submitted to the blockchain.

@@

Our approach aims to alleviate the expensive gas comsuming by distributing the negation of the assertion to validators.

Each validator endeavors to find a counterexample of the assertion using this negation. Specifically, each validator attempts to find a counterexample by identifying $a \in A$ such that the negation formula is satisfied $\neg P_{a}$. When a counterexample is found, the validator submits it, which is then re-verified on-chain.

Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points. Since only one specific point is checked on-chain, the amount of gas required for the computation to check the counterexample is likely to be significantly less than verifying the entire assertion directly on-chain.

%In this distributed process, each validator attempts to identify a counterexample to the assertion. Upon finding one, the validator submits the counterexample on-chain. Consequently, instead of verifying the entire assertion, the on-chain contract only needs to check specific points.

@@

Each validator try to find  a
random $n$ in the range $2 \le n \le 
\sqrt p$ such that $(p \mathbin{\%} n) = 0$. If the remainder is $0$, the validator found a counterexample.

An other example, consider a contract that takes a sorted array of integers.
\begin{lstlisting}[numbers=none]
contract Sorted {
  function find (int[50] a, int v) public {
    // assume a is sorted
  }
}
\end{lstlisting}
The explicit assertion would be
\begin{gather}\label{eq:1}
  (\forall k) (0\le k <49) \Rightarrow a[k] \le a[k+1]
\end{gather}
While we can check this contract in $O(1)$ time, the constant factor is big! So we
consider its negation.
\begin{displaymath}
  (\exists k) (0\le k <49) \wedge a[k] > a[k+1]
\end{displaymath}
Each validator attempts to find the number $k$ such that the negation is true for such $k$, then the validator has found a counterexample for the sortedness of the array.

\section{Proof-of-work-based incentivization method}
Finding a counterexample is rewarded, incentivizing validators, but comes at the cost of computing resources. Instances of finding a counterexample may be rare, as callers typically avoid passing invalid parameters into the blockchain. If no counterexample emerges, the verification accuracy depends on the number of wisepoints generated to negate the assertion, with more validators increasing the certainty.

Encouraging validators to engage in the verification process even without discovering a counterexample is crucial. Therefore, it is necessary to incentivize this effort. %Moreover, it is logical to reward only a portion of the computational effort required. 
However, to prioritize the discovery of counterexamples, the reward for finding a counterexample is set significantly higher than that for providing a computational proof.

We propose a proof-of-work-based incentivization method in which validators are rewarded for discovering counterexamples, and some are rewarded for their computational efforts, thus encouraging participation in the distributed verification process.
\subsection{Outlines}
A significant concern arises regarding how to ensure that validators perform the verification computation off-chain, even when no counterexample is foundward.

We propose a proof-of-work-based method to incentivize participants in the distributed verification process.  The proposed approach is outlined as follows:
\begin{itemize}
%\item There are two ways to reward validators to encourage their participation: to discover a counterexample, and to provide computational proof that they have executed the program to search for a counterexample, even if none is found.
\item We utilize the proof-of-work concept by introducing a target hash $t$ that sets the required difficulty level to earn the computation reward. 
\item The objective of the validator is to find a computation proof that smaller than or equal to the target hash $t$.
\item The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.
\end{itemize}
%Because the rewards may be limited in quantity, validators are motivated to swiftly verify the parameters to claim the reward before others do so. 
\subsection{Computation proof}
The next question is how to devise a computational proof to incentivize computational effort. The key challenge is how to involve the negation check in the computational proof and how to reproduce the computational proof off-chain to on-chain with a reasonable gas cost. To address this, we introduce a seed $s$ in each verification process.

Let \( n \) denote the size of the domain \( A \). Each number \( i \) in the range \([1, n]\) corresponds to an element in \( A \). The seed \( s \) is a random number, and we can reduce it modulo \( n \) to obtain \( i \), which is associated with an element \( a \) in \( A \).

\paragraph{Estimate the number of seeds:} We first estimate the number of seeds needed to find a counterexample with a given expected probability.

Let's assume the unsatisfied element is only at the first element $a_0$ in $A$, the size of the domain is $n$, and the number of seeds is $m$. Each seed independently has a probability of $1/n$ to detect the problem and a probability of $\frac{n-1}{n}$ not to detect the problem. Hence, if we assume that each seed associated with an element $a$ in $A$ is chosen independently from a uniform distribution, the probability that no seed checks the element $a_0$ converges to $0$ as the number of seeds approaches infinity:

@@

Depending on the expected probability to detect the problem, the number of seeds to generate can be determined.

Assume that $p$ is the probability of finding at least one counterexample. The complementary probability is used to calculate the number of seeds $m$ needed to achieve a given expected probability $p$ of finding a counterexample.
\begin{itemize}
\item The probability of a single seed failing to find a counterexample is $\frac{n-1}{n}$.
\item The probability of all $m$ seeds failing to find a counterexample is $\left(\frac{n-1}{n}\right)^m$.
\item The probability of at least one of the $m$ seeds finding a counterexample is:
\[
p = 1 - \left(\frac{n-1}{n}\right)^m
\]
\end{itemize}

@@

\[
\frac{2^{256} - 1}{m}
\]
\paragraph{Conduct a computation proof:} The computation of the negation formula is integrated into the computational proof to ensure that the validators cannot produce the proof without executing a negation check.

Lets \(\text{eval}\) be the function that returns the significant components of the evaluation of the negation \(\neg P_{a}\).  For example, it returns \(a[i]\) and \(a[i + 1]\) in the evaluation of the negation predicate \(a[i] < a[i+1]\) in the sorted array example.

Thus, the computation hash includes the seed  \( s \) and \(\text{eval}\). 
\begin{align}
t_s = \text{hash}(s, \text{eval}(\neg P_{a}))
\end{align}
\paragraph{Find a seed:}
The sequence of operations to find a seed can be described by the following steps:
\begin{enumerate}
\item Generate a random seed $s$: 
\begin{align}
s \in \mathbb{N} 
\end{align}
where $s$ is a random natural number.
\item Calculate $n$ as the size of the domain $A$: 
\begin{align}
n = |A|
\end{align}
where $\mid A \mid$ denotes the number of elements in the domain $A$.
\item Determine $i \in [1, n]$ using the modulo operation:
\begin{align}
i = (s \mod n) + 1
\end{align}
\item Find the corresponding element $a$ in $A$:
\begin{align}
a=A[i]
\end{align}
where $A[i]$ denotes the $i$-th element in $A$.
\item Perform the negation check $\neg P_{a}$ to detect a counterexample if any.

\item If no counterexample is found, calculate the hash \( t_s \) corresponding to the seed \( s \).
\item Compare \( t_s \) to the target hash to determin whether it is a reward computation.
\end{enumerate}

\begin{comment}
\begin{tikzpicture}[node distance=2cm]

    % Nodes
    \node (start) [startstop] {Generate random seed $s$};
    \node (calc_n) [process, below of=start] {Calculate $n = |A|$};
    \node (calc_i) [process, below of=calc_n] {Determine $i = (s \mod n) + 1$};
    \node (find_a) [process, below of=calc_i] {Find $a = A[i]$};
    \node (neg_check) [process, below of=find_a] {Perform negation check $\neg P_a$};
    \node (counterexample) [decision, below of=neg_check, yshift=-1cm] {Counterexample found?};
    \node (calc_hash) [process, below of=counterexample, yshift=-1cm] {Calculate hash $t_s$};
    \node (compare) [process, below of=calc_hash] {Compare $t_s$ to target hash};
    \node (non_reward) [startstop, right of=counterexample, xshift=3cm] {No Counterexample};
    \node (reward) [startstop, right of=compare, xshift=3cm] {Reward Computation};
    \node (submit) [process, below of=compare, yshift=-1cm] {Submit on-chain to claim reward};
    \node (submit_counter) [process, below of=counterexample, yshift=-1cm] {Submit on-chain to claim reward};

    % Arrows
    \draw [arrow] (start) -- (calc_n);
    \draw [arrow] (calc_n) -- (calc_i);
    \draw [arrow] (calc_i) -- (find_a);
    \draw [arrow] (find_a) -- (neg_check);
    \draw [arrow] (neg_check) -- (counterexample);
    \draw [arrow] (counterexample) -- node[anchor=east] {Yes} (submit_counter);
    \draw [arrow] (counterexample) -- node[anchor=south] {No} (calc_hash);
    \draw [arrow] (calc_hash) -- (compare);
    \draw [arrow] (compare) -- node[anchor=south] {No} (non_reward);
    \draw [arrow] (compare) -- node[anchor=south] {Yes} (reward);
    \draw [arrow] (reward) |- (submit);
    \draw [arrow] (submit_counter) -| (submit);

\end{tikzpicture}
\end{comment}
%Consequently, each seed $s$ is linked with an element $a$ in the domain $A$, followed by the evaluation of the negation of the assertion $\neg P_{a}$.

@@

\begin{enumerate}
\item Front-running attacks: The system is vulnerable to front-running attacks, where an attacker closely monitors the mempool to intercept a seed representing a counterexample or a computation proof, subsequently stealing the reward.
\item Caller exploitation: A caller might exploit the system by running the negation check privately to identify the reward before submitting the parameter on-chain, thereby swiftly claiming the reward ahead of the other validators. 
\item Denial-of-service (DoS) attacks: The system is susceptible to DoS attacks, where a caller inundates the system with numerous invalid parameters, causing congestion and hindering its operation.
%\item Reward manipulation: A validator may attempt to manipulate the reward system by resubmitting counterexamples or computation proofs multiple times to multiply their rewards.
\end{enumerate}
\subsection{Overview architect}
This section presents a practical model that unifies theoretical principles and addresses the previously mentioned security concerns. The architectural design of this model is depicted in Figure \ref{fig.architect}. The model consists of two main entities: an on-chain assertion contract and off-chain validator contract. In our practical model, three distinct actors play key roles.
\begin{itemize}
\item[•] Owner: responsible for deploying and overseeing both on-chain and off-chain contracts.
\item[•] Callers: engage with on-chain contracts by initiating assertions and interacting with the system.
\item[•] Validators: tasked with validating parameters and ensuring the integrity of the verification process.
\end{itemize}

@@

%In some applications, multiple computational proofs may be allowed. This record is crucial for determining when a work function can be invoked for a given parameter or when it should be discarded.

@@

For our offline distributed verification method, let's assume that the parameter is valid, and now we consider the cost to verify the parameter and perform the actual work. %Let $m$ be the number of proofs required to ensure the correctness of the parameter. 
Thus, the offline method costs the gas for submitting the parameter, the gas to store the parameter (or its hash), the gas to submit the seed, check the condition of the parameter point associated with the seed, the gas to compute the hash and compare it with the target hash, and of course the gas to run the computation of the actual work.

@@

\begin{equation}
G_{off} = G_{parameter} + G_{storage} +   (G_{seed} + G_{check} + G_{hash}) + G_{run}
\end{equation}

\begin{itemize}
    \item \( G_{parameter} \): Intrinsic gas for submitting the parameter.
    \item \( G_{storage} \): Gas for storing the parameter or its hash.
    \item \( G_{seed} + G_{check} + G_{hash} \): Gas for 
    \begin{itemize}
        \item Submit the seed (\( G_{seed} \)).
        \item Check the condition of the parameter point associated with the seed (\( G_{check} \)).
        \item Compute the hash and compare it with the target hash (\( G_{hash} \)).
    \end{itemize}
    \item \( G_{run} \): Gas for performing the actual work (computation).
\end{itemize}

@@

\paragraph*{Parameter Checking}
\begin{itemize}
    \item In the on-chain method, the parameter check cost is \( n \cdot G_{check} \), where \( n \) is the size of the parameter.
    \item In the offline method, this cost is \( G_{check} \).
\end{itemize}

\paragraph*{Additional Costs in the Offline Method}
\begin{itemize}
    \item The offline method includes \(  G_{seed} \) for submitting each seed.
    \item It also includes \(  G_{hash} \) for computing and comparing hashes, which the on-chain method does not explicitly incur.
\end{itemize}

@@

Since the centralize verification process only costs in term of gas and the distrbiuted process uses the proof of work incentive, we converts the reward in term of gas. Lets $G_{reward}$ be the gas, which is price for finding the proof. Let \( G_{proof} \) be the sum of the gas costs to perform and reward the  computation proof. 
\[
G_{proof} = G_{seed} + G_{check} + G_{hash} + G_{reward} 
\]

In case the base gas does not contain the storage gas, then the \( G_{proof} \) gas includes it.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \begin{axis}[
        title={Gas Consumption Chart},
        xlabel={Parameter size},
        ylabel={Gas},
        grid=both,
        major grid style={line width=.2pt,draw=gray!50},
        minor grid style={line width=.1pt,draw=gray!20},
        xtick={1,2,3,4,5,6,7,8},
        xticklabels={1,2,3,,,,n,},
        ytick={1,2,3,4,5,6,7,8},
        yticklabels={$G_{base} + G_{check}$,$G_{base} + 2 \cdot G_{check}$, $G_{base} + 3 \cdot G_{check}$,,$G_{base}+ G_{proof}$,,$G_{base} + n \cdot G_{check}$,},
    ]
      \addplot[
        color=red,
        mark=square,
        ]
        coordinates {
        (1,1)(2,2)(3,3)(4,4)(5,5)(6,6)(7,7)
        };
        % Add custom labels as nodes
      %\node at (axis cs:1,1) [anchor=north] {$(1, m)$};
      %\node at (axis cs:2,2) [anchor=north] {$(2, g_3)$};
      %\node at (axis cs:3,3) [anchor=north] {$(3, a)$};
      %\node at (axis cs:4,4) [anchor=north] {$(4, b)$};
      %\node at (axis cs:5,5) [anchor=north] {$(5, c)$};

@@

%          \addplot[
%         color=blue,
%         mark=square,
%         ]
%         coordinates {
%         (1,5)(2,5)(3,5)(4,5)(5,5)(6,5)(7,5)
%         };
%     \end{axis}
%   \end{tikzpicture}
%   \caption{Gas comparation (non-storage)}
%   \label{fig:gas_compare_nonstorage}
% \end{figure}
Overall, the offline method (\( G_{off} \)) is generally more cost-effective for large parameters as it reduces the number of on-chain checks from \( n \) to 1. However, the exact cost-effectiveness depends on the relative sizes of \( n \), the parameter storing gas, and the specific gas costs of \( G_{seed} \), \( G_{hash} \) and \( G_{reward} \).
\section{Domain Specification Language for Assertion}
\note{To discuss: if it make sense to design}
\section{Converter - Generating an Assertion Contracts} 
\note{To discuss: if it make sense to implement}
\section{Prototype Implementations}
\note{TODO}
\subsection{Sorted array}
%There are two possible data structures for storing such records: map and array. For example, if we assume that a caller can submit only one parameter at a time, we can use a map that associates the caller's address with the parameter's hash and timestamp.
%\begin{lstlisting}[numbers=none]
%   struct Parameter {
%        bytes32 p_hash;
%        uint256 timestamp;
%    }
% mapping (address => Parameter) public parameters;
%\end{lstlisting}
